Higher-Order unification for free!

### 2024-07-01 paper/main.tex
"so that the code of (𝑚𝑎𝑙𝑙𝑜𝑐) below can preserve" what can it preserve?
Plus I removed a line break to not exceed the 12 pages

\noindent
A solution to a \Fo{} variable is, instead, a plain term, that is, \elpiIn{fsubst}
is an abbreviation for \elpiIn{mem to}.
%We call \elpiIn{fsubst} the memory of \Fo{}, while we call \elpiIn{subst}
%the one of \Ho.

The compiler establishes a mapping between variables of the two languages.

@@

\noindent
Each \elpiIn{mvariable} is stored in the mapping together with
its arity (a number) so that the code of \ref{clause:malloc} below can preserve:

>>>>

\noindent
A solution to a \Fo{} variable is, instead, a plain term, that is, \elpiIn{fsubst}
is an abbreviation for \elpiIn{mem to}.
%We call \elpiIn{fsubst} the memory of \Fo{}, while we call \elpiIn{subst}
%the one of \Ho.
%
The compiler establishes a mapping between variables of the two languages.

@@

\noindent
Each \elpiIn{mvariable} is stored in the mapping together with
its arity (a number) so that the code of \ref{clause:malloc} below can preserve
the following property:
